%!TEX root = ../report.tex
\begin{thebibliography}{9}

\bibitem{suzuki}
	Satoshi Suzuki, Keiichi Abe,
	\emph{Topological structural analysis of digitized binary images by border following},
	Computer Vision, Graphics, and Image Processing 30, 32-46,
	1985.

\bibitem{results1}
	System performance,
	\emph{\url{https://www.youtube.com/watch?v=-adBxIIIo1k}}

\bibitem{results2}
	System simulation in RobWork,
	\emph{\url{https://www.youtube.com/watch?v=-adBxIIIo1k}}

\bibitem{kalman}
	R. E. Kalman,
	\emph{A New Approach to Linear Filtering and Prediction Problems},
	Journal of Basic Engineering 82, (Series D): 35-45,
	1960.

\bibitem{RRTConnect}
	James J. Kuffner, Jr., Steven M. LaValle,
	\emph{RRT-Connect: An Efficient Approach to Single-Query Path Planning},
	Proc. 2000 IEEE Int’l Conf. on Robotics and Automation,ICRA, 2000.

\bibitem{Zhang}
	Zhengyou Zhang,
	\emph{Flexible Camera Calibration By Viewing a Plane From Unknown Orientations},
	Microsoft Research, One Microsoft Way, Redmond, WA 98052-6399, USA
	1998.

\bibitem{Hartley}
	Richard Hartley, Andrew Zisserman
	\emph{Multiple View Geometry in Computer Vision},
	$2^{\circ}$ Edition, Cambridge.

\bibitem{Brown}
	Duane C. Brown
	\emph{Decentering Distortion of Lenses},
	D. Brown Associates, Inc.

\bibitem{kalman_lectures}
	Dirk Kraft
	\emph{An Introduction to Tracking Techniques}
	Robotics and Computer Vision 2, SDU, 2015

\bibitem{OReilly}
	Gary Bradski and Adrian Kaehler
	\emph{Learning OpenCV}
	OReilly Media, Inc., First edition

\bibitem{Yaobi}
	\emph{YAOBI, Yet Another OBB-Tree implementation},
	http://yaobi.sourceforge.net/

\end{thebibliography}
